DIAGNOSTIC SUPPORT OF SKIN LESION CLASSIFICATION USING CNN AND SOFT ATTENTION

### 2022-08-15 MDPI/Sensor Paper/template.tex
Update Paper

\subsection{Related Works}
Skin lesion classification is not a new area, since there are many great performance models constructed. One of the most cutting-edge technologies that have been used is Soft-Attention as stated in\cite{03358}. Soumyyak et al construct several models formed by the combination of a backbone model including DenseNet201\cite{06993}, InceptionResNetV2\cite{00567}, ResNet50\cite{03385}\cite{05027}, VGG16\cite{1556} and Soft-Attention layer. Using those above backbones has been tried by many previous papers. Rishu Garg et al \cite{03798} uses transfer learning approach with CNN based model. Amirreaza et al \cite{10348} do not only use those above backbone model but also used InceptionV3\cite{00567} model. Another paper that uses the backbone models is \cite{09418}, Hemanth et al decide to use EfficientNet\cite{11946} and SeNET\cite{01507} instead and CutOut\cite{04552v2} method which involves creating holes of different sizes on the images i.e. technically making a random portion of image inactive during data augmentation process. \cite{01284} also used Deep Convolution Neural Network, Peng Yao et al used RandArgument which crops an image into several images from a fixed size, DropBlock which is used for regularization, Multi-Weighted New Loss which is used for dealing with the imbalanced data problem, end-to-end Cumulative Learning Strategy which can more effectively balance representation learning and classifier learning without additional computational cost. Another state of the art is GradCam and Kernel SHAP\cite{06612}, Kyle Young et al create model agnostic, local interpretable methods that can highlight pixels that the trained network deems relevant for the final classification.

Otherwise, there are also many state of the art whose great performance on skin lesion classification. The Student and Teacher Model is also a high performance model in 2021\cite{03225}, which is created by Xiaohan Xing et al as the combination of two model which share the memory with each other. Therefore, they can take full advantage of what others learn. SkinLinkNet\cite{12602} and WonderM\cite{03426} are both tested the effect of segmentation on skin lesion classification problem created by Amirreza et al and Yeong Chan et al, respectively. In WonderM, the method used is padding the image so that the image has the shape increased from (450,600) to (600, 600). In SkinLinkNet, instead resize the image down to (448, 448). Both of SkinLinkNet and WonderM use UNet to do the segmentation task, though they use EfficientNetB0 and DenseNet to do the classification task, respectively. Another approach is using metadata including gender, age, and capturing position as stated in \cite{03910} by Nil Gessert et al.

@@

\FloatBarrier
\begin{table}[ht]
	\centering
	\begin{tabular}{|p{1cm}|p{12.5cm}|}
		\hline
		Work & Approach \\ 
		\hline
		\cite{03358} & Combination of Backbone Model and Soft Attention. Backbone model includes DenseNet201, InceptionResNetV2, VGG16, ResNet50, ResNet34\\
		\hline
		\cite{03798} & Transfer Learning with CNN based model\\
		\hline
		\cite{10348} & Transfer Learning with CNN based model including DenseNet201, InceptionResNetV2, VGG16, ResNet50, ResNet34, and InceptionNetV3\\
		\hline
		\cite{09418} & Transfer Learning with CNN based model including EfficientNet and SeNet. Data augmentation process used CutOut to create random sized hole considered as an inactive portion of image.\\
		\hline
		\cite{01284} & Transfer Learning with CNN based model. Data augmentation process uses RandArgument to split picture into several pictures which is used to train. DropBlock and Multi-Weight Loss Function are used to deal with the imbalanced.\\
		\hline
		\cite{06612} & GradCam and Kernel SHAP, two model agnostic, local interpretable methods that can highlight pixels that the trained network deems relevant for the final classification.\\
		\hline
		\cite{03225} & Student and Teacher Model is the combination of two model which share the memory learned with others. \\
		\hline
		\cite{12602} & SkinLinkNet uses the image whose shape is (448,488) for training. Unet and EfficientNetB0 are used for segmentation and classification task respectively.\\
		\hline
		\cite{03426} & WonderM uses the image whose shape is (600,600) created by padding for training. Unet and DenseNet are used for segmentation and classification task respectively.\\
		\hline
		\cite{03910} & MetaData including age, gender, and capture position are used to gain higher performance of the model. The models used in this paper are CNN-based model \\
		\hline
		\cite{03798} & Traditional Machine Learning Algorithms are applied including Random Forest, XGBoost, and Support Vector Machine \\
		\hline
		\cite{10348} & Matrix Factorization are applied before the softmax activation function \\
		\hline
		\cite{05045} & Isolation Forest are applied distribution skin lesion images before fedding into the softmax activation function. \\
		\hline
		\cite{10348} & Matrix Factorization are applied before the softmax activation function. \\
		\hline
	\end{tabular}
	\caption{Related Works Summary. This table is a summary of the approach to skin lesion classification and segmentation. The first column illustrate the cite to the paper research. Column 2 shows a brief summary of the method that is stated in the associated paper.}
	\label{table:related-work-summary}
\end{table}
\FloatBarrier
\subsection{Objectives}
In this paper, the effect of metadata on classifying skin disease will be analyzed. On the other hand, by analyzing the combination of several backbone models, I will also construct an optimized model that has the ability to classify in a balanced way between classes instead of well identifying the majority of classes.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Materials and Methods}
\subsection{Data}
\subsubsection{Image Data}
The data set used in this paper is the HAM10000 data set published by Havard University Dataverse\cite{10417}. There are total 7 classes in this data set containing Actinic keratoses and intraepithelial carcinoma or Bowen's disease (AKIEC), Basal cell Carcinoma (BCC),  benign keratosis-like lesions (solar lentigines / seborrheic keratoses andchen-planus like keratoses, BKL), dermatofibroma (DF), melanoma (MEL), melanocytic nevi (NV), and vascular lesions (angiomas, angiokeratomas, pyogenic granulomas and hemorrhage, VASC). The distribution of the data set is shown in the table below:

@@

More than 50 percent of lesions are confirmed through histopathology (HISTO), the ground truth for the rest of the cases is either follow-up examination (FOLLOWUP), expert consensus (CONSENSUS), or confirmation by in-vivo confocal microscopy (CONFOCAL). On the other hand, before being used for training the whole data is shuffled then split into two part. $90$ percent and $10$ percent of the data is used for training and validating respectively.

In the previous research\cite{03358}, the image data is augmented for all class, the number of image increase to 18015 images. Since, this data is imbalanced, using augmented data may cause the problem of well classify on the classes almostly taking the number of samples. In this paper, instead of augmenting data, metadata is used. The way of processing metadata is discussed in MetaData section. Images in this data set has the type of $RGB$ and shape of (450, 600). However, Each backbone need the different input size of image as well as the range of pixel value. DenseNet201\cite{06993} require the input pixels values are scaled between $0$ and $1$ and each channel is normalized with respect to the ImageNet data set. In Resnet50 and Resnet152\cite{03385}\cite{05027}, the images are converted from $RGB$ to $BGR$, then each color channel is zero-centered with respect to the ImageNet data set, without scaling. InceptionResNetV2\cite{11946}, on the other hand, will scale input pixels between $-1$ and $1$. Similarly, three versions of MobileNet\cite{04861}\cite{04381}\cite{02244}, NasNetMobile and NasNetLarge\cite{07012} require the input pixel is in range of $-1$ and $1$.

\subsubsection{Metadata}
The HAM10000 data set\cite{10417} also contain the metadata of patient including gender, age, and the capturing position as well as the test data set containing 857 images. During the data exploration term, the age category miss 57 data points, which is decided to remove this 57 samples. In the gender and capturing position category contain some samples of unknown. Instead of removing, these "unknowns" data points is kept and considered as "prefer not to say". Besides, the label of the whole data is preprocessed into one-hot vector.
\subsection{Model Schema}
\subsubsection{Input Schema}
Using metadata as another input is not new. In paper\cite{03910}, they decide to keep the missing value and set its value to $0$. The sex and anatomical site are categorical encoded. The age, on the other hand is numerical normalized. After processing, the metadata is fed into a two-layer neural network with 256 neurons each. Each layer contains batch normalization, a ReLU\cite{08375} activation, and dropout with $p = 0.4$. The network’s output is concatenated with the CNN’s feature vector after global average pooling. Especially, they use a simply data augmentation strategy to address the problem of missing values in metadata. During training, they randomly encode each property as missing with a probability of $p = 0.1$.

@@

\subsubsection{Soft-Attention}
Applying the Soft-Attention layer in deep learning is not a new approach. Soft-Attention has been used in various applications: image caption generation in \cite{03044} and handwriting verification in \cite{202017} respectively. In skin lesion classification, Soft-Attention is used to increase the performance of the model as described in \cite{03358}. Soft-Attention can ignore irrelevant areas of the image by multiplying the corresponding feature maps with low weights. The function below describes the flow of the Soft-Attention module:
\[
f_{sa} = \gamma t\sum_{k=1}^{K}softmax(W_k * t)
\]
In order to apply Soft-Attention, there are two main steps. Firstly, the input tensor is put in grid-based feature extraction from the high-resolution image, where each grid cell is analyzed in the whole slide to generate a feature map\cite{08513}. This feature map called $t \in R^{h \times w \times d}$ where $h, w, \text{and } d$ is the shape of tensor generated by a Convolution Neural Network(CNN), is then input to a 3D convolution layer whose weights is $W_k \in R^{h \times w \times d \times K}$. The output of this convolution is normalized using the softmax function to generate K = 16 attention maps. These $16$ attention maps are aggregated to produce a weight function called $\alpha$. This $\alpha$ function is then multiplied with feature tensor $t$ and scaled by $\gamma$, a learnable scalar. Finally, the output of Soft-Attention function $f_{sa}$ is the concatenation of the beginning feature tensor $t$ and the scaled attention maps.

@@

After feeding into ReLU function layer, the feature map is processed in two paths. The first path is the 2-dimensional Max Pooling. In the second path, the feature map, on the other hand is fed into the Soft-Attention Layer before the 2-dimensional Max Pooling. After all, these two paths are then concatenated, fed into a ReLU layer, and a Dropout with the probability of $0.5$.
\subsubsection{Backbone Model Architecture}
In this paper, the backbone models used in this paper are DenseNet201\cite{06993}, Inception\cite{00567}, MobileNets\cite{04861}\cite{04381}\cite{02244}, ResNet\cite{03385}\cite{05027}, and NasNet\cite{07012}. The combination of DenseNet201, InceptionResNetV2 and Soft-Attention layer are both tested by the previous paper\cite{03358} with a great performance. Otherwise, Resnet50 also well classify but with much less number of parameter and depth than based on its f1-score and precision stated. Therefore, in this paper, the performance of the model Resnet152 and NasnetLarge which has the larger number of parameter and depth is analyzed. On the other hand, three version of MobileNet and the NasnetMobile will also be analyzed which has a small number of parameter and depth.

\subsubsection{Model}
The whole architecture of the model used for image feature extraction is applied in the same way in paper \cite{03358}. Metadata branch, otherwise is preprocessed before feeding into a dense layer then concatenate with the output of Soft-Attention layer. It is described in the figure below:

\begin{figure}[H]
	\centering
	\includegraphics[width=0.5\linewidth]{Definitions/MainModel - Model Form}
	\caption{Overall Mobile-based Model Architecture}
	\label{fig:main-model}
\end{figure}

\subsection{Loss Function}
The loss function used in this paper is categorical cross-entropy. Consider $X = [x_1, x_2, \dots, x_n]$ as the input feature, $\theta = [\theta_1, \theta_2, \dots, \theta_n]$. Let $N$, and $C$ is the number of training examples and number of class respectively. The categorical cross-entropy loss is presented as:
\[L(\theta, x_n) = -\frac{1}{N}\sum_{c=1}^{C}\sum_{n=1}^{N}W_c\times y^c_n \times \log(\hat{y}^c_n)\]
where $\hat{y}^c_i$  is the output of model and $y^c_i$ is the target that the model should return, $W_c$ is the weight of class $c$. Since the data set face the imbalanced problem then I applied the class weight for the loss. This formula below is used to calculate the class weight:
\[W = N \odot D\]
\[D = \begin{bmatrix}
	\frac{1}{C \times  N_1} & \frac{1}{C \times  N_2} & \dots & \frac{1}{C \times  N_n}\\
\end{bmatrix} = \frac{1}{C} \odot \begin{bmatrix}
	\frac{1}{N_1} & \frac{1}{N_2} & \dots & \frac{1}{N_n}\\
\end{bmatrix}\]
where $N$ is the number of training sample, $C$ is the number of class, $N_i$ is the number of sample in each class $i$. $D$ is the matrix contain the inverse of $C \times N_i$. 
\subsection{Evaluation Metrics}
\begin{figure}[!htb]
	\begin{minipage}{0.48\textwidth}
		\centering
		\includegraphics[width=1.1\linewidth]{Definitions/Confusion-matrix}
		\caption{Confusion Matrix}\label{fig:confusion-matrix}
	\end{minipage}\hfill
	\begin{minipage}{0.48\textwidth}
		\centering
		\includegraphics[width=.7\linewidth]{Definitions/AUC}
		\caption{Area Under the Curve}\label{fig:AUC}
	\end{minipage}
\end{figure}
In this paper, the model is evaluated by using the confusion matrix and related metrics. The figure 4 illustrates the presentation of a $2 \times 2$ confusion matrix used for $2$ class. Consider a confusion matrix $A$ with $C$ number of class. Let $A^i$ and $A^j$ is the set of $A$ rows and columns respectively. 
\[
A = \begin{bmatrix}
	a_{11} & a_{12} & \dots & a_{1j} \\
	a_{21} & a_{22} & \dots & a_{2j} \\
	\vdots & \vdots	&  & \vdots\\
	a_{i1} & a_{i2} & \dots & a_{ij} 
\end{bmatrix}
\]

The True Positive(TP) of all class in this case is the main diagonal of the matrix $A$. The following method are used to calculate the False Positives(FP), False Negatives(FN), and True Negatives(TN) of all class:
\[
FP = -TP + \sum_{k=1}^{i}A^i_k \hspace{1cm} FN = -TP + \sum_{k=1}^{j}A^j_k
\]
\[
TN_c = \sum_{i=1}^{C}\sum_{j=1}^{C}a_{ij} - \left[ \sum_{k=1}^{i}A^i_{i=c k} + \sum_{k=1}^{j}A^j_{j=c k} \right] + a_{i=c j=c} \implies TN = \begin{bmatrix}
	TN_1 & TN_2 & \dots & TN_c
\end{bmatrix}
\]
Then, the model is evaluated by the following metrics:
\[\text{Sensitivity(Sens)} = \frac{TP}{TP + FN} \hspace{1cm} \text{Specificity(Spec)} = \frac{TN}{TN + FP}\]
\[\text{Precision} = \frac{TP}{TP + FP} \hspace{1cm} \text{F1 Score} = \frac{2 \times TP}{2 \times TP + FP + FN + TN}\]
\[\text{Accuracy} = \frac{TP + TN}{TP + FP + FN + TN} \hspace{1cm} \text{Balanced Accuracy} = \frac{\text{Sens} + \text{Spec}}{2}\]
The last metric is the $AUC$ score standing for Area Under the Curve which is the Receiver Operating Curve(ROC) that indicate the probability of TP versus the probability of FP.  
\subsection{Traning}
Before training, the data set is split into three sub datasets including training, validation, and testing. In this paper, the graphic card that is used to train is Nvidia RTX TitanV. In order to make the comparison fair, all the model in this paper is trained with Adam Optimizer\cite{6980}. The initial learning rate is set to $0.001$, an learning rate reduction schedule is setup with the minimum learning rate is $0.0000001$ with the factor of $0.2$, the epsilon argument of the optimizer is set to $0.1$. On the other hand, Early Stopping is also set up, if the accuracy of validation set does not increase after 25 epochs, the training will stop.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Results}
The accuracy of all model is presented in the figure below:

@@

\begin{table}[H]
	\centering
	\begin{tabular}{| c | c | c | c | c |}
		\hline
		InceptionResNetV2 & DenseNet201 & ResNet50 & Resnet152 & MobileNetV2\\
		\hline
		0.89 & 0.89 & 0.70 & 0.57 & 0.81\\
		\hline
	\end{tabular}
\end{table}

>>>>

\subsection{Related Works}
Skin lesion classification is not a new area, since there are many great performance models constructed. One of the most cutting-edge technologies that have been used is Soft-Attention as stated in\cite{03358}. Soumyyak et al construct several models formed by the combination of a backbone model including DenseNet201\cite{06993}, InceptionResNetV2\cite{00567}, ResNet50\cite{03385}\cite{05027}, VGG16\cite{1556} and Soft-Attention layer. Their approach is to add the Soft-Attention layer at the end or the middle of the backbone model. For ResNet50 and VGG16, the Soft-Attention layer is added after the third residual block and CNN block, respectively. DenseNet201 and InceptionResNetV2, otherwise concatenate with the Soft-Attention before a fully-connected layer, and then soft-max layer.

Using those above backbones has been tried by many previous papers. Rishu Garg et al \cite{03798} uses transfer learning approach with CNN based model: ResNet50 and VGG16 which are pretrained with ImageNet data set. Besides, they also use data augmentation to avoid the imbalance of the data set. Histogram Equalization is also used to increase the contrast of the skin lesions before feeding into the Machine Learning algorithms including Random Forest, XGBoost, Support Vector Machine.

Amirreaza et al \cite{10348} do not only use those above backbone model but also used InceptionV3\cite{00567} model. In that research, the dataset HAM10000 and $PH^2$ are combined to create a 8 classes data set. Before feeding into the Deep CNN models, the image is resized to (224, 224) for DenseNet201, ResNet152, InceptionResNetV2 and (229, 229) for InceptionV3.

Another paper that uses the backbone models is \cite{09418}, Hemanth et al decide to use EfficientNet\cite{11946} and SeNET\cite{01507} instead and CutOut\cite{04552v2} method which involves creating holes of different sizes on the images i.e. technically making a random portion of image inactive during data augmentation process.

Otherwise, \cite{01284} also used Deep Convolution Neural Network, Peng Yao et al used RandArgument which crops an image into several images from a fixed size, DropBlock which is used for regularization, Multi-Weighted New Loss which is used for dealing with the imbalanced data problem, end-to-end Cumulative Learning Strategy which can more effectively balance representation learning and classifier learning without additional computational cost.

Another state of the art is GradCam and Kernel SHAP\cite{06612}, Kyle Young et al create model agnostic, local interpretable methods that can highlight pixels that the trained network deems relevant for the final classification. In that research they use three data sets containing HAM10000, BCN-20000 and MSK. Before feeding into the models, the images are preprocessed by binarized with a very low threshold to find the center of mass.

On the other hand, there are also many state of the art whose great performance on skin lesion classification. The Student and Teacher Model is also a high performance model in 2021\cite{03225}, which is created by Xiaohan Xing et al as the combination of two model which share the memory with each other. Therefore, they can take full advantage of what others learn.

SkinLinkNet\cite{12602} and WonderM\cite{03426} are both tested the effect of segmentation on skin lesion classification problem created by Amirreza et al and Yeong Chan et al, respectively. In WonderM, the method used is padding the image so that the image has the shape increased from (450,600) to (600, 600). In SkinLinkNet, instead resize the image down to (448, 448). Both of SkinLinkNet and WonderM use UNet to do the segmentation task, though they use EfficientNetB0 and DenseNet to do the classification task, respectively.

Another approach is using metadata including gender, age, and capturing position as stated in \cite{03910} by Nil Gessert et al. The metadata is fed into fully connected neural network after being encoded into one-hot vector. All missing data point of age is set to 0. In order to overcome the missing data problem, the research apply one-hot encoding to the group but the initial validation is poor performance then numerical encoding is applied.

@@

\begin{table}
	\centering
	\begin{tabular}{| c | p{1.5cm} | p{1.5cm} | p{2cm} | p{1.5cm} | p{2cm} |}
		\hline
		Research & Deep Learning & Machine Learning & Data 
		Augmentation & Feture Extraction & Data set\\
		\hline
		\cite{03358} & x & & x & & HAM10000\\
		\hline
		\cite{03798} & x & x & x & x & HAM10000\\
		\hline
		\cite{10348} & x & x & x & & HAM10000, $PH^2$\\
		\hline
		\cite{09418} & x & & x & & HAM10000\\
		\hline
		\cite{01284} & x & & x & & HAM10000\\
		\hline
		\cite{06612} & x & & x & x & HAM10000, BCN-20000, MSK\\
		\hline
		\cite{03225} & x & & x & & HAM10000\\
		\hline
		\cite{12602} & x & & x & & HAM10000\\
		\hline
		\cite{03426} & x & & x & & HAM10000\\
		\hline
		\cite{03910} & x & & x & & HAM10000\\
		\hline
		\cite{05045} & & x & x & x & HAM10000\\
		\hline
	\end{tabular}
	\caption{Related Works Summary. This table is a summary of the approach to skin lesion classification and segmentation. The first column illustrate the cite to the paper research. Column 2 shows a brief summary of the method that is stated in the associated paper.}
	\label{table:related-work-summary}
\end{table}
\subsection{Proposed Method}
In this research, a new model is constructed from the combination of:\\
- Backbone model including DenseNet201, InceptionResNetV2, ResNet50/152, NasNetLarge, NasNetMobile, and MobileNetV2/V3\\
- Using metadata including age, gender, localization as another input of the model\\
- Using Soft-Attention as a feature extractor of the model\\
- A new weight loss function
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Materials and Methods}
\subsection{Materials}
\subsubsection{Image Data}
The data set used in this paper is the HAM10000 data set published by Havard University Dataverse\cite{10417}. There are total 7 classes in this data set containing Actinic keratoses and intraepithelial carcinoma or Bowen's disease (AKIEC), Basal cell Carcinoma (BCC),  benign keratosis-like lesions (solar lentigines / seborrheic keratoses andchen-planus like keratoses, BKL), dermatofibroma (DF), melanoma (MEL), melanocytic nevi (NV), and vascular lesions (angiomas, angiokeratomas, pyogenic granulomas and hemorrhage, VASC). The distribution of the data set is shown in the table below:

@@

More than 50 percent of lesions are confirmed through histopathology (HISTO), the ground truth for the rest of the cases is either follow-up examination (FOLLOWUP), expert consensus (CONSENSUS), or confirmation by in-vivo confocal microscopy (CONFOCAL). On the other hand, before being used for training the whole data is shuffled then split into two part. $90$ percent and $10$ percent of the data is used for training and validating respectively. Images in this data set has the type of $RGB$ and shape of (450, 600). However, Each backbone need the different input size of image as well as the range of pixel value.

\subsubsection{Metadata}
The HAM10000 data set\cite{10417} also contain the metadata of patient including gender, age, and the capturing position 
\begin{table}[H]
	\centering
	\begin{tabular}{|c c c c |} 
		\hline
		ID & Age & Gender & Local\\ 
		\hline
		ISIC-00001 & 15 & Male & back\\
		\hline
		ISIC-00002 & 85 & Female & elbow\\
		\hline
	\end{tabular}
	\caption{Metadata example in the data set}
	\label{table:metadata sample}
\end{table}
\subsection{Methodology}
\subsubsection{Overall Architecture}
The whole architecture of the model used for image feature extraction is applied in the same way in paper \cite{03358}. Metadata branch, otherwise is preprocessed before feeding into a dense layer then concatenate with the output of Soft-Attention layer. It is described in the figure below:

\begin{figure}[H]
	\centering
	\includegraphics[width=1\linewidth]{Definitions/MainModel - Model Form}
	\caption{Overall Model Architecture}
	\label{fig:main-model}
\end{figure}

\subsubsection{Input Schema}
In this research, the image data is both augmented for all class, the number of image increase to 18015 images and keep original form. Before feeding into the backbone model, the images is pre-processed by the input requirement of each model. DenseNet201\cite{06993} require the input pixels values are scaled between $0$ and $1$ and each channel is normalized with respect to the ImageNet data set. In Resnet50 and Resnet152\cite{03385}\cite{05027}, the images are converted from $RGB$ to $BGR$, then each color channel is zero-centered with respect to the ImageNet data set, without scaling. InceptionResNetV2\cite{11946}, on the other hand, will scale input pixels between $-1$ and $1$. Similarly, three versions of MobileNet\cite{04861}\cite{04381}\cite{02244}, NasNetMobile and NasNetLarge\cite{07012} require the input pixel is in range of $-1$ and $1$.

On the other hand, the metadata is also used as another input. In paper\cite{03910}, they decide to keep the missing value and set its value to $0$. The sex and anatomical site are categorical encoded. The age, on the other hand is numerical normalized. After processing, the metadata is fed into a two-layer neural network with 256 neurons each. Each layer contains batch normalization, a ReLU\cite{08375} activation, and dropout with $p = 0.4$. The network’s output is concatenated with the CNN’s feature vector after global average pooling. Especially, they use a simply data augmentation strategy to address the problem of missing values in metadata. During training, they randomly encode each property as missing with a probability of $p = 0.1$.

@@

\subsubsection{Backbone Model}
In this paper, the backbone models used in this paper are DenseNet201\cite{06993}, Inception\cite{00567}, MobileNets\cite{04861}\cite{04381}\cite{02244}, ResNet\cite{03385}\cite{05027}, and NasNet\cite{07012}. The combination of DenseNet201, InceptionResNetV2 and Soft-Attention layer are both tested by the previous paper\cite{03358} with a great performance. Otherwise, Resnet50 also well classify but with much less number of parameter and depth than based on its f1-score and precision stated. Therefore, in this paper, the performance of the model Resnet152 and NasnetLarge which has the larger number of parameter and depth is analyzed. On the other hand, three version of MobileNet and the NasnetMobile will also be analyzed which has a small number of parameter and depth.

\subsubsection{Soft-Attention}
Applying the Soft-Attention layer in deep learning is not a new approach. Soft-Attention has been used in various applications: image caption generation in \cite{03044} and handwriting verification in \cite{202017} respectively. In skin lesion classification, Soft-Attention is used to increase the performance of the model as described in \cite{03358}. Soft-Attention can ignore irrelevant areas of the image by multiplying the corresponding feature maps with low weights. The function below describes the flow of the Soft-Attention module:
\[
f_{sa} = \gamma t\sum_{k=1}^{K}softmax(W_k * t)
\]
In order to apply Soft-Attention, there are two main steps. Firstly, the input tensor is put in grid-based feature extraction from the high-resolution image, where each grid cell is analyzed in the whole slide to generate a feature map\cite{08513}. This feature map called $t \in R^{h \times w \times d}$ where $h, w, \text{and } d$ is the shape of tensor generated by a Convolution Neural Network(CNN), is then input to a 3D convolution layer whose weights is $W_k \in R^{h \times w \times d \times K}$. The output of this convolution is normalized using the softmax function to generate K (a constant value) attention maps. These $K$ attention maps are aggregated to produce a weight function called $\alpha$. This $\alpha$ function is then multiplied with feature tensor $t$ and scaled by $\gamma$, a learnable scalar. Finally, the output of Soft-Attention function $f_{sa}$ is the concatenation of the beginning feature tensor $t$ and the scaled attention maps.

@@

After feeding into ReLU function layer, the feature map is processed in two paths. The first path is the 2-dimensional Max Pooling. In the second path, the feature map, on the other hand is fed into the Soft-Attention Layer before the 2-dimensional Max Pooling. After all, these two paths are then concatenated, fed into a ReLU layer, and a Dropout with the probability of $0.5$.

\subsubsection{Loss Function}
The loss function used in this paper is categorical cross-entropy. Consider $X = [x_1, x_2, \dots, x_n]$ as the input feature, $\theta = [\theta_1, \theta_2, \dots, \theta_n]$. Let $N$, and $C$ is the number of training examples and number of class respectively. The categorical cross-entropy loss is presented as:
\[L(\theta, x_n) = -\frac{1}{N}\sum_{c=1}^{C}\sum_{n=1}^{N}W_c\times y^c_n \times \log(\hat{y}^c_n)\]
where $\hat{y}^c_i$  is the output of model and $y^c_i$ is the target that the model should return, $W_c$ is the weight of class $c$. Since the data set face the imbalanced problem then I applied the class weight for the loss. This formula below is used to calculate the class weight:
\[W = N \odot D\]
\[D = \begin{bmatrix}
	\frac{1}{C \times  N_1} & \frac{1}{C \times  N_2} & \dots & \frac{1}{C \times  N_n}\\
\end{bmatrix} = \frac{1}{C} \odot \begin{bmatrix}
	\frac{1}{N_1} & \frac{1}{N_2} & \dots & \frac{1}{N_n}\\
\end{bmatrix}\]
where $N$ is the number of training sample, $C$ is the number of class, $N_i$ is the number of sample in each class $i$. $D$ is the matrix contain the inverse of $C \times N_i$.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Results}
\subsection{Experimental Setup}
\subsubsection{Training}
Before training, the data set is split into two sub set for training (90 percent) and validation (90 percent). Test set, otherwise is provided by the HAM10000 data set, contains 857 images. In order to analyze the effect of augmented data on the model, during the training the image data is augmented by the following technique:\\
- Rotation Range: rotate the image in a fixed angle. \\
- Width and height shift range: Shift the image horizontally and vertically, respectively. \\
- Zoom Range: zoom in the image to create new image. \\
- Horizontal and vertical flipping: flipping the image horizontally and vertically to create new form of image.\\
Otherwise, all of models is trained with the Adam Optimizer \cite{6980} with the learning rate of $0.001$ which is reduced by a factor of $0.2$ to a minimum learning rate of $0.1 x 10^6$, and the epsilon is set to $0.1$. The initial epochs is set to 250 epochs and the Early Stopping is also applied to stop the training as the accuracy of validation set does not increase after $25$ epochs. Besides, the batch size is set to $32$.

\subsubsection{Tools}
In order to build and train the model, Keras and TensorFlow library are applied. In detail, Keras is used to build, clone the backbone model which is pre-trained with the image-net data set. Soft-Attention, on the other hand is coded by inheriting the Layer class of TensorFlow. Therefore, the Soft-Attention layer can be combined with the functional API model. Otherwise, the models are trained by NVIDIA RTX TitanV and the data set is pre-processed with the CPU Intel I5 32 processors, RAM 32GB. In detail, the GPU is setup with CUDA 11.6, cuDNN 8.3 and ChipSRT as the requirement of TensorFlow.
\subsubsection{Evaluation Metrics}
\begin{figure}[!htb]
	\begin{minipage}{0.48\textwidth}
		\centering
		\includegraphics[width=1.1\linewidth]{Definitions/Confusion-matrix}
		\caption{Confusion Matrix}\label{fig:confusion-matrix}
	\end{minipage}\hfill
	\begin{minipage}{0.48\textwidth}
		\centering
		\includegraphics[width=.7\linewidth]{Definitions/AUC}
		\caption{Area Under the Curve}\label{fig:AUC}
	\end{minipage}
\end{figure}
In this paper, the model is evaluated by using the confusion matrix and related metrics. The figure 4 illustrates the presentation of a $2 \times 2$ confusion matrix used for $2$ class. Consider a confusion matrix $A$ with $C$ number of class. Let $A^i$ and $A^j$ is the set of $A$ rows and columns respectively. 
%\[
%A = \begin{bmatrix}
%	a_{11} & a_{12} & \dots & a_{1j} \\
%	a_{21} & a_{22} & \dots & a_{2j} \\
%	\vdots & \vdots	&  & \vdots\\
%	a_{i1} & a_{i2} & \dots & a_{ij} 
%\end{bmatrix}
%\]
The True Positive(TP) of all class in this case is the main diagonal of the matrix $A$. The following method are used to calculate the False Positives(FP), False Negatives(FN), and True Negatives(TN) of all class:
\[
FP = -TP + \sum_{k=1}^{i}A^i_k \hspace{1cm} FN = -TP + \sum_{k=1}^{j}A^j_k
\]
\[
TN_c = \sum_{i=1}^{C}\sum_{j=1}^{C}a_{ij} - \left[ \sum_{k=1}^{i}A^i_{i=c k} + \sum_{k=1}^{j}A^j_{j=c k} \right] + a_{i=c j=c} \implies TN = \begin{bmatrix}
	TN_1 & TN_2 & \dots & TN_c
\end{bmatrix}
\]
Then, the model is evaluated by the following metrics:
\[\text{Sensitivity(Sens)} = \frac{TP}{TP + FN} \hspace{1cm} \text{Specificity(Spec)} = \frac{TN}{TN + FP}\]
where Sensitivity and specificity mathematically describe the accuracy of a test which reports the presence or absence of a condition. Individuals for which the condition is satisfied are considered "positive" and those for which it is not are considered "negative". Sensitivity or true positive rate refers to the probability of a positive test, conditioned on truly being positive while Specificity  or true negative rate refers to the probability of a negative test, conditioned on truly being negative.
\[\text{Precision} = \frac{TP}{TP + FP} \hspace{1cm} \text{F1 Score} = \frac{2 \times TP}{2 \times TP + FP + FN + TN}\]
Precision or positive predictive value (PPV) is the probability of a positive test conditioned on both truly being positive or negative. F1-score, on the other hand refers the harmonic mean of precision and recall which mean the higher the f1-score is, the higher both precision and recall is. Besides, the expected value of precision, f1-score and recall-score are also applied because of the multi-class problem.
\[\text{Accuracy} = \frac{TP + TN}{TP + FP + FN + TN} \hspace{1cm} \text{Balanced Accuracy} = \frac{\text{Sens} + \text{Spec}}{2}\]
The last metric is the $AUC$ score standing for Area Under the Curve which is the Receiver Operating Curve (ROC) that indicate the probability of TP versus the probability of FP.

\subsection{Discussion} 
The accuracy of all model is presented in the figure below:

@@

\begin{table}[H]
	\centering
	\begin{tabular}{| c | c | c | c | c |}
		\hline
		InceptionResNetV2 & DenseNet201 & ResNet50 & Resnet152 & MobileNetV2\\
		\hline
		0.90 & 0.89 & 0.70 & 0.57 & 0.81\\
		\hline
	\end{tabular}
\end{table}
